Introduction to LLL\\``Cryptography''

### 2021-06-02 paper.tex
Implement ECDSA attack with lots of nonce
ECDSA attack explained known bits nonce

\[
B = 
\begin{pmatrix}
    X^3 & f_2X^2 & f_1X & f_0 \\
    0 & NX^2 & 0 & 0 \\
    0 & 0 & NX & 0 \\
    0 & 0 & 0 & N \\
\end{pmatrix}
\]

@@

@@

\textbf{Lattice construction}. We construct the lattice

\[
    B = 
    \begin{pmatrix}
        n & 0 & 0 \\
        t & 1 & 0 \\
        u & 0 & K \\
    \end{pmatrix}
\]

The vector $v = (-k_1, k_2, K)$ is in the lattice because

\[
    v = (tk_2 + u - xn = -k_1, k_2, K)
\]

@@

This method is described better in

@@

>>>>

\[
B = 
\begin{pmatrix}
    X^3 & f_2X^2 & f_1X & f_0 \\
    0 & NX^2 & 0 & 0 \\
    0 & 0 & NX & 0 \\
    0 & 0 & 0 & N
\end{pmatrix}
\]

@@

\subsection{Recover $d$ from a pair of signatures with small $k_1, k_2$}

@@

\textbf{Lattice construction}. We construct the lattice $B = (b_0, b_1, b_2)$:

\[
    B = 
    \begin{pmatrix}
        n & 0 & 0 \\
        t & 1 & 0 \\
        u & 0 & K
    \end{pmatrix}
\]

Note that the vector $v = (-k_1, k_2, K)$ is in the lattice because

\[
    v = -xb_0 + k_2b_1 + b_2 = (-xn + tk_2 + u = -k_1, k_2, K)
\]

@@

In this case if we apply LLL in the second row we obtain:

\begin{center}
    $v = (-k_1, k_2, K) = (\texttt{-0x50a65330, 0x1f5b977a, 0x100000000})$
\end{center}

To retrieve $d$ we just need to compute

\[
    d = r_1^{-1}(k_1s_1 - h_1) = \texttt{0xf00e5fb275bfd304}
\]

Source of the method:

@@

\subsection{Recover $d$ from many signatures}

Suppose we have many signatures $(r_1, s_1), \ldots, (r_m, s_m)$ with message hashes $h_1, \ldots, h_m$. We can write the equivalence
$s_i \equiv k_i^{-1}(h_i +  dr_i) \mod n$ for $i = 1,\ldots,m$ and we can remove $d$ as before to get

\[
\begin{array}{c}
    k_1 + t_1k_m + u_1 \equiv 0 \mod n \\
    k_2 + t_2k_m + u_2 \equiv 0 \mod n \\
    \vdots \\
    k_{m-1} + t_{m-1}k_m + u_{m-1} \equiv 0 \mod n
\end{array}
\]

And create the lattice $B$ as

\[
    B = 
    \begin{pmatrix}
     n &  \\
     & n \\
     & & \ddots \\
     & & & n \\
     t_1 & t_2 & \cdots & t_{m-1} & 1 & 0 \\
     u_1 & u_2 & \cdots & u_{m-1} & 0 & K
     \label{eq:lattice_ecdsa}
    \end{pmatrix}
\]

Same as before this lattice contains $v = (-k_1, -k_2, \ldots, k_m, K)$ and with probability TODO we can find that vector after applying LLL.

\subsection{Recover $d$ knowing MSB bits from each $k$}

What if we know the firsts MSB bits of each $k_i$?

Well, we can write $k_i = (a_i + b_i)$, where $a_i$ is the known part and $b_i$ is the unkown part that satisfies $|b_i| < K$. If we plug these values
into the equivalence we obtain

\[
    \begin{array}{c}
        k_i + t_ik_m + u_i \equiv 0 \mod n \\
        (a_i + b_i) + t_i(a_m + b_m) + u_i \equiv 0 \mod n \\
        b_i + t_ib_m + a_i + t_ia_m + u_i \equiv 0 \mod n \\
    \end{array}
\]

And we can set $u_i' = a_i + t_ia_m + u_i$ to be the value inside the lattice \ref{eq:lattice_ecdsa} instead of $u_i$. In this way the vector

\begin{center}
    $v = (-b_1, -b_2, \ldots, b_m, K)$
\end{center}

is in the lattice and could be found using LLL. To recover the original $(k_1, \ldots, k_m)$ we must add to $v$ the vector $w = (a_1, \ldots, a_m)$.

I was able to recover the nonces with the $10$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures, but it's also possible
to recover the nonces with less known bits as shown in \href{https://eprint.iacr.org/2020/1540}{paper}.
